\addsymbol {\alpha_x}: {The segment position coordinate for a mapped control layer vertex $x$.}{alpha}
\addsymbol {b}: {The number of bits used to represent a quantised pixel.}{bits}
\addsymbol {d_x}: {A distance or displacement value for the point $x$.}{distance}
\addsymbol {\varepsilon}: {Quantisation error.}{quanterror}
\addsymbol {J_x}: {A joint plane for joint $x$.}{jointplane}
\addsymbol {\vec{j}_x}: {A joint location in a skeleton structure.}{joint}
\addsymbol {\cal N}: {The set of all normal volumes for a triangle mesh.}{nvset}
\addsymbol {N_x}: {The normal volume associated with the triangle $t_x$ in a mesh.}{nv}
\addsymbol {\hat{n}_x}: {The normal  $\in {\mathbb R}^3$ of vertex $x$ in a mesh.}{normal}
\addsymbol {\vec{p}_x}: {The position $\in {\mathbb R}^3$ of an arbitrary point $x$.}{point}
\addsymbol {q_i}: {A quantised pixel in an image.}{quantpixel}
\addsymbol {r}: {The range of values stored in a displacement map.}{range}
\addsymbol {\cal S}_n: {The dimensionality of a segment with $n+1$ bounding planes.}{segdim}
\addsymbol {\cal T}: {The set of all triangles in a mesh.}{tris}
\addsymbol {t_x}: {A triangle with index $x$ in a mesh.}{triangle}
\addsymbol {\vec{u}_{tx}}: {A texture coordinate $\in {\mathbb R}^2$ for a vertex $x$ of a face t.}{texcoord}
\addsymbol {\cal V}: {The set of all vertices in a mesh.}{verts}
\addsymbol {\vec{v}_x}: {The position $\in {\mathbb R}^3$ of vertex $x$ in a mesh.}{vertex}
\addsymbol {\omega_x}: {An areal coordinate component corresponding to the point $\vec{p}_x$.}{areal}
\addsymbol {\hat{v}}: {A normalised version of a vector $\vec{v}$ (i.e. has unit length).}{normvector}
\addsymbol {x}: {An index\symbol{x}.}{x}
